

```{r}
#Load the dataset and view the data

library(readxl)
Adm <- read_excel("C:/Users/indir/Desktop/Rutgers MBA/Analytics for BI/Project/Adm.xlsx")
```

```{r}
colnames(Adm)[colnames(Adm)=="GRE Score"] <- "GREScore"
colnames(Adm)[colnames(Adm)=="TOEFL Score"] <- "TOEFLScore"
colnames(Adm)[colnames(Adm)=="University Rating"] <- "UniversityRating"
colnames(Adm)[colnames(Adm)=="Chance of Admit"] <- "ChanceofAdmit"
colnames(Adm)
```

```{r}
#Remove Serial No Column
Adm<-Adm[,c(2,3,4,5,6,7,8,9)]
```

```{r}
data <- Adm
View(data)
```

```{r}
#Create a new Admit column and fill it with 1 if ChanceofAdmit >0.70 else 0
data$Admit<-ifelse(data$ChanceofAdmit>0.70,"1","0")
data$Admit <- as.factor(data$Admit)
View(data)
```

```{r}
#Split data into train and test in 70-30 ratio
Atrain<-sample(nrow(data),nrow(data)*0.70)
data.train<-data[Atrain,]
data.test<-data[-Atrain,]
```

```{r}
View(data.train)
View(data.test)
nrow(data.train)
nrow(data.test)
```

```{r}
train.X = data.train[,c(1,2,3,4,5,6,7)]
test.X = data.test[,c(1,2,3,4,5,6,7)]
train.Admit = data.train$Admit
test.Admit = data.test$Admit
```
```{r}
View(train.X)
View(test.X)
View(train.Admit)
```

```{r}
#k=2
library(class)
set.seed(1)
knn.pred = knn(train.X, test.X, train.Admit, k=2)
table2 = table(knn.pred, test.Admit)
table2
# Accuracy =(32+52)/(32+14+22+52)= 70%
```
```{r}
#k=3
library(class)
set.seed(1)
knn.pred = knn(train.X, test.X, train.Admit, k=3)
table3 = table(knn.pred, test.Admit)
table3
# Accuracy = (44+55)/120 = 82.5%
```

```{r}
#k=4
library(class)
set.seed(1)
knn.pred = knn(train.X, test.X, train.Admit, k=4)
table4 = table(knn.pred, test.Admit)
table4
# Accuracy = (43+55)/120= 81.7%
```
```{r}
#Check only using the significant features from regression
train2.X = data.train[,c(1,5,6,7)]
test2.X = data.test[,c(1,5,6,7)]
train2.Admit = data.train$Admit
test2.Admit = data.test$Admit``
```{r}
#k=2
library(class)
set.seed(1)
knn.pred2 = knn(train2.X, test2.X, train2.Admit, k=2)
table22 = table(knn.pred2, test2.Admit)
table22
#Accuracy = 75%
```

```{r}
#k=3
library(class)
set.seed(1)
knn.pred2 = knn(train2.X, test2.X, train2.Admit, k=3)
table23 = table(knn.pred2, test2.Admit)
table23
#Accuracy = 98/120 = 81.7%
```

```{r}
#k=4
library(class)
set.seed(1)
knn.pred2 = knn(train2.X, test2.X, train2.Admit, k=4)
table24 = table(knn.pred2, test2.Admit)
table24
#Accuracy = 99/120 = 82.5%
```
```{r}
library(gplots)
my_palette <- colorRampPalette(c("lightblue", "lightgreen"))(n = 299)

knn.pred2_heatmap <- heatmap.2(table2,Rowv=NA, Colv=NA, col=my_palette, scale="column", margins=c(5,10),cellnote=table2,notecol="black",main="Classification Matrix for K=2",xlab="Admit Test",ylab="Admit Predicted")
```
```{r}
knn.pred3_heatmap <- heatmap.2(table3,Rowv=NA, Colv=NA, col=my_palette, margins=c(6,10),cellnote=table3,notecol="black",main="Classification Matrix for K=3",xlab="Admit Test",ylab="Admit Predicted")
```

```{r}
knn.pred4_heatmap <- heatmap.2(table4,Rowv=NA, Colv=NA, col=my_palette, scale="column", margins=c(5,10),cellnote=table4,notecol="black",main="Classification Matrix for K=4",xlab="Admit Test",ylab="Admit Predicted")
```

